---
title: "p8105_hw5_ms6358.Rmd"
output: github_document
---

```{r}
library(tidyverse)
```

## Create a city_state variable

```{r}
homicide_df = 
  read.csv("./homicide-data.csv", na = c("","unknown")) %>%
  mutate(
    city_state = str_c(city,state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"
    )) %>%
  relocate(city_state) %>%
  filter(city_state != "TulsaAL")
```

##  Use the prop.test function to estimate the proportion of homicides that are unsolved

```{r}
baltimore_df =
  homicide_df %>%
  filter(city_state == "BaltimoreMD")

baltimore_summary =
  baltimore_df %>%
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

baltimore_test = 
  prop.test(
  x = baltimore_summary %>% pull(unsolved),
  n = baltimore_summary %>% pull(n)
)

baltimore_test %>%
  broom::tidy()
```

## Run prop.test for each of the cities

```{r}
prop_test_function = function(city_df) {
  
city_summary =
  city_df %>%
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

city_test = 
  prop.test(
  x = city_summary %>% pull(unsolved),
  n = city_summary %>% pull(n)
)

return(city_test)
}

results_df = 
  homicide_df %>%
  nest(data = uid:resolution) %>%
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>%
  unnest(tidy_results) %>%
  select(city_state, estimate, starts_with("conf"))
```

```{r}
results_df %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low,ymax = conf.high))
  theme(axis.title.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) 
```

## Summarize within cities to obtain the total number of homicides and the number of unsolved homicides

```{r}
homicide_df %>%
  group_by(city_state) %>%
  summarise(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>%
  mutate(
    test_results = map2(unsolved, n, prop.test),
    tidy_results = map(test_results, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>%
  unnest(tidy_results) %>%
  select(city_state, estimate, starts_with("conf"))
```

Problem 2

## Create a dataframe

```{r}
file_df = tibble(
  file = list.files("data")
)

read_function = function(file){
  path = str_c("data/",file)
  data = read_csv(path)
  return(data)
}

participant_df = 
  file_df %>% 
  mutate(
    data = purrr::map(file,read_function)
    )
```

## Tidy the result

```{r}
participant_df =
  participant_df %>%
  mutate(
    control_arm = substr(file,1,3),
    subject_id = substr(file,5,6)
    ) %>% 
  relocate(subject_id,control_arm) %>% 
  select(-file) %>% 
  unnest(data) %>%
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "value"
  ) %>% 
  mutate(
    week=as.numeric(week)
  ) 
```

## Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}
participant_df %>% 
  ggplot(aes(x = week,y=value,color = subject_id)) +
  geom_point()+
  geom_line()+
  facet_grid(.~control_arm)
```

As the plots shown above, the values of exposed group are generally higher than those of control group. And even though there is fluctuation in both groups, the values of each subject in control group mostly ended up with the value close to that at the begining. However, in terms of exposed group, there is obivious increasing after 8-week period.

Problem 3

## Download the dataset

```{r}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

## Write a function

```{r}
replace_function = function(vector){
    if(is.numeric(vector)){
      replace_value = mean(vector, na.rm=TRUE)
    }
  else if(is.character(vector)){
      replace_value = "virginica"
    }
  replace_na(vector,replace_value)
}

iris_df =
  iris_with_missing %>% 
  map_df(replace_function)
```